---
title: "Symbolix Demo"
author: "Kohleth Chia"
date: "20 June 2017"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background
The PV system app I made <http://kohleth.shinyapps.io/solarappv2> has a statistical model that predicts PV generation for a given suburb at a given date. This repository contains scripts to update that predictive model to use a new batch of data which I have collected in the past year, as well as more advanced modelling techniques. This project has a fairly strong machine-learning flavour, as opposed to the more traditional statistical analysis.

## Repository Contents
There are 3 R scripts.

* `formData.R` -- forms the data for modelling. The output is stored in `pv.rds`.
* `plotCluster.R` -- produces a visualization of the postcode cluster (formed in `formData.R`) as a visual check.
* `trainModel_v1.R` -- the main script which trains the new models. Also see the [Modelling](#model) section.

And two R objects.

* `pv.rds` -- the output of `formData.R`. So this script need not be re-run again (running it requires dataset which I have not uploaded to this repository.)
* `vic.rds` -- dataset containing spatial information for the visualization task in `plotCluster.R`. Again, having this eliminates the need to upload the rather large shape file to this repository.

## Modelling{#model}
Suburbs in VIC are grouped into clusters, and a separate model is trained for each cluster. 
`trainModel_v1.R` uses the `caret` package to train a `glmnet`, `Cubist`, `SVM`, and `bam` (Big Generalized Additive model with splines), using OOB bootstrap as resampling scheme. The model with the lowest RMSE is the best. 

Once the model is trained, unnecessary parts of the model object is trimmed (removed) so that in deploy time, a smaller object can be loaded.

## P.S.
<<<<<<< HEAD
Just when I am about to send this, I realized Symbolix made `googleway`, so as a salute to your company. Below is my route to your interview tomorrow. (can't really show this )

```{r,cache=TRUE}
library(googleway)
source("mykey.R")

origin="Hallam Station"
destination="1A/14 Akuna Drive Williamstown North VIC 3016"

df <- google_directions(origin = origin,
                        destination = destination,
                        key = mykey,
                        arrival_time=as.POSIXct("2017-06-21 09:30:00 AEST"),
                        mode = "transit",
                        simplify = TRUE)
pl=data.frame(polyline=df$routes$overview_polyline$points)

google_map(key = mykey, search_box = T) %>%
  add_polylines(data = pl, polyline = "polyline", stroke_weight = 9)
```

![route](route.tiff)

